### 2023-04-18 glossaries/links.tex
Add conferences

>>>>

\newlink{conf-filachange}{Filachange Workshop}{https://www.swot-adac.org/news-and-events/filachange-workshop}
\newlink{conf-egu22}{EGU 2022}{https://meetingorganizer.copernicus.org/EGU22/EGU22-8668.html}
\newlink{conf-carbon}{Ocean Carbon from Space Workshop}{https://oceancarbonfromspace2022.esa.int/}
\newlink{conf-egu21}{EGU 2021}{https://meetingorganizer.copernicus.org/EGU21/EGU21-4178.html}
\newlink{conf-lapcod}{LAPCOD 2019}{https://lapcod.rsmas.miami.edu/2019-Venice/index.php?page=home}
